Robust Fault-Tolerant Control and Motion Planning of UAVs and Biped Robots Team System for Search and Rescue Usage

### 2022-10-27 paper/paper.tex
Add couple term to paper. Finish the uav+robots animation.

\section{PRELIMINARIES OF S\&R URTS}
The URTS will start with a given S\&R area, and end with mission completed. The URTS is composed of $N_T$ teams and a ground station. Each team contains $N_A$ agents with $1$ UAV and $N_A-1$ robots. Hence, the $i$th agent in the $j$th team is denoted as $\alpha_{j,i}$, where $i=1,2,...,N_A$ and $j=1,2,...,N_T$. The UAVs are chosed as the first agents in each team, i.e., $\alpha_{1,j}$. Each agent has environmental sensing capability and load capability, while the ground station is responsible for computing and decision-making. Besides, there are communication channels between agents and ground station through wireless network.
% The system architecture if URTS is shown in Fig. \ref{fig:1}.
% \begin{figure}[htbp]
% \centering
% \includegraphics[width=0.4\textwidth]{fig/1.pdf}\caption{System structure of URTS}%
% \label{fig:1}
% \end{figure}

@@

\section{Reference Tracking control}
After the reference trajectory $r(t)$ is set, the last step is to design a controller for an agent to track it. To analyze the tracking control problem of UAV model in (\ref{eq:uav}) and robot model in (\ref{eq:robot}) together, we represent them by the same form called agent model through some appropriate variable transformations:
\begin{equation} \label{eq:agent} 
    M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) = u(t)
where $u(t)\in\mathbb{R}^n$ is control input vector, $x(t)\in\mathbb{R}^n$ is state vector, $M(\cdot)\in\mathbb{R}^{n\times n}$ is inertia matrix, and $H(\cdot, \cdot)\in\mathbb{R}^n$ is non-inertial force vector. The control law is given as:
\begin{equation} \label{eq:control}
    u(t)= M(r(t))(\ddot{r}(t) + u_{fb}(t)) + H(r(t),\dot{r}(t)) 
where $M(r(t)),\ddot{r}(t),H(r(t),\dot{r}(t))$ are the feedfoward control terms for canceling system nonlinearity, and $u_{fb}(t)$ is the feedback control law for improving system robustness. To make the model more realistic, the following external disturbances encountered in actual scenarios are considered:
\begin{enumerate}
    \item For agent, there exists coupling effect due to co-channel interference in communication between agents \cite{9448458}.
    \item For agent, there exists cyber-attack on communication network between agents and ground station.
    \item For agent, there exists sensor noise.
    \item For UAV, there exists wind disturbance \cite{9075385}.
    \item For robot, there exists ground reaction force \cite{chen2013human}. 
\end{enumerate}
Since the ground station is responsible for the calculation, the calculated control command (\ref{eq:control}) will be transmitted to the agent through the network channel in URTS. Therefore, the coupling effect due to co-channel interference and the cyber-attack signal will deteriorate the control command. In addition, the wind disturbance and the ground reaction force will apply extra force on an agent (\ref{eq:agent}). Therefore, through appropriate conversion, the above disturbances can be equivalent to a disturbance force $d_1(t)$. The nominal system (\ref{eq:agent}) then be rewrited as the following real system:
% The coupling effect for an agent \textit{$agent_{i,j}$} in URTS can be expressed as the form $\sum_{i'=1,i'\neq i}^{N_i}\sum_{j'=1,j'\neq j}^{N_j}\textit{c}_{i,j}(x_{i,j}(t))\times x_{i',j'}(t)$ where $x_{i,j}(t)$ is the own state.
\begin{equation} \label{eq:agent d1} 
    M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) = u(t) + d_1(t)
% \subsubsection{Internal uncertainties}
% In practice, there is uncertaintiey in the parameters of inertia matrix $M$, Coriolis and centripetal force vector $C$, gravitational force vector $G$, and friction vector $F$. Its effect can be expressed as:
% \begin{equation} \label{eq:internal}
%         &M = M_0 + \Delta M, C = C_0 + \Delta C
%         \\
%         &G = G_0 + \Delta G, F = F_0 + \Delta F
% where $M_0, C_0, G_0$ and  $F_0$ is the nominal part and $\Delta M,\Delta C,\Delta G$ and $\Delta F$ is the uncertain part.
Now, substituting (\ref{eq:control}) into (\ref{eq:agent d1}) and subtracting $M(x(t))\ddot{r}(t)$ from the left and right sides, we have:
\begin{equation} \label{eq:agent1}
        & M(x(t))(\ddot{x}(t)-\ddot{r}(t)) + H(x(t),\dot{x}(t)) \\
        & =(M(r(t))-M(x(t)))\ddot{r}(t) + M(r(t))u_{fb}(t) \\
        & + H(r(t),\dot{r}(t)) + d_1(t)
By Multipling $M(x(t))^{-1}$ from the left and right sides and with some arrangments, we have:
\begin{equation} \label{eq:error, state eq}
    \ddot{e}(t) = u_{fb}(t) + f_1(t)
where $f_1(t) = M(x(t))^{-1}(-\Delta M (\ddot{r}(t)+u_{fb}(t)) -\Delta H + d_1(t))\in\mathbb{R}^n$ is the actuator fault signal, $\Delta M \triangleq M(x(t)) - M(r(t)), \Delta H \triangleq H(x(t),\dot{x}(t)) - H(r(t),\dot{r}(t))$ are the error terms from feedforward compensation, and $e(t)= x(t)-r(t)$ is the tracking error.
%         Although the error terms $\Delta e$, $\Delta M$ and $\Delta H$ caused by the difference between state $x(t)$ and estimated state $\hat{x}(t)$ are not necessarily bounded, they can still be estimated as long as they are smooth.
Let $\pmb{e}(t)=\begin{bmatrix}
    \int_{0}^{t}e^T(\tau)d\tau & e^T(t) & \dot{e}^T(t)
\end{bmatrix}^T\in\mathbb{R}^{3n}$ be the PID tracking error, (\ref{eq:error, state eq}) can be rewrited as:
\begin{equation} \label{eq:linear f1}
    \dot{\pmb{e}}(t)=A\pmb{e}(t)+B(u_{fb}(t)+f_1(t))
where $ A = A_0\otimes I_n, B = B_0\otimes I_n$
with $A_0 = \begin{bmatrix}
    0 & 1 & 0 \\ 0 & 0 & 1 \\ 0 & 0 & 0
\end{bmatrix}, B_0 = \begin{bmatrix}
0 \\ 0 \\ 1

@@

\textit{agents:}\begin{enumerate}
    \item system parameters: $C_0 = I_3$, $B_{2,0} = [0, 0.1, 1]^T$.
    \item designed parameters: $Q_1 = 50*diag(diag(1,100,10),\allowbreak 0, 0), Q_2 = 5*diag(diag([1,100,10]), diag(1,0.1,\allowbreak 0.01), diag(1,0.1,0.01 ,0.001)), R=0.002, \rho=30$. Actuator and sensor smoothing signal model window sizes are $3$ and $4$, respectively.
\end{enumerate}

@@

\textit{robots:} \begin{enumerate}
    \item system parameters: Appendix E in \cite{ourrobot}. Initial values $\bar{x}_0=$.
    \item designed parameters: $Q_1=,Q_2=,R=,rho=20$.
\end{enumerate}

@@

\textit{UAV:}
The trajectories of reference, state and estimated state are shown in Fig. \ref{fig:UAV, state}. The estimation of actuator fault $f_1(t)$ is shown in Fig. \ref{fig:UAV, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t)=10\sin(3t)$. The estimation of sensor fault $f_2(t)$ is shown in Fig. \ref{fig:UAV, fs} where $f_2(t)$ is set as a smoothed square wave as shown in figure. The control effort is shown in Fig. \ref{fig:UAV, control}.
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The trajectories of reference, state and estimated state of the UAV $\alpha_{i,1}$}%
    \label{fig:UAV, state}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of actuator fault of the UAV $\alpha_{i,1}$}
    \label{fig:UAV, fa}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of snesor fault of the UAV $\alpha_{i,1}$}%
    \label{fig:UAV, fs}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The control effort of the UAV $\alpha_{i,1}$}%
    \label{fig:UAV, control}
\end{figure}

\textit{robot:}
The trajectories of reference, state and estimated state are shown in Fig. \ref{fig:robot, state}. The estimation of actuator fault $f_1(t)$ is shown in Fig. \ref{fig:robot, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t)=\sin(3t)$. The estimation of sensor fault $f_2(t)$ is shown in Fig. \ref{fig:robot, fs} where $f_2(t)$ is set as a smoothed square wave as shown in figure. The control effort is shown in Fig. \ref{fig:robot, control}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{i,2}$}%
    \label{fig:robot, state}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of actuator fault of the robot $\alpha_{i,2}$.}%
    \label{fig:robot, fa}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of sensor fault of the robot $\alpha_{i,2}$}%
    \label{fig:robot, fs}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The control effort of the robot $\alpha_{i,2}$}%
    \label{fig:robot, control}
\end{figure}

>>>>

\section{PRELIMINARIES OF S\&R URTS}
The URTS will start with a given S\&R area, and end with mission completed. The URTS is composed of $N_T$ teams and a ground station. Each team contains $N_A$ agents with $1$ UAV and $N_A-1$ robots. Hence, the $j$th agent in the $i$th team is denoted as $\alpha_{i,j}$, where $i=1,2,...,N_T$ and $j=1,2,...,N_A$. The UAVs are chosed as the first agents in each team, i.e., $\alpha_{i,1}$. Each agent has environmental sensing capability and load capability, while the ground station is responsible for computing and decision-making. Besides, there are communication channels between agents and ground station through wireless network.
% The system architecture if URTS is shown in Fig. \ref{fig:1}.
% \begin{figure}[htbp]
% \centering
% \includegraphics[width=0.4\textwidth]{fig/1.pdf}\caption{System structure of URTS}%
% \label{fig:1}
% \end{figure}

@@

\section{Reference Tracking control}
After the reference trajectory $r(t)$ is set, the last step is to design a controller for an agent to track it. To analyze the tracking control problem of UAV model in (\ref{eq:uav}) and robot model in (\ref{eq:robot}) together, we represent them by the same form called agent model through some appropriate variable transformations:
\begin{equation} \label{eq:agent} 
    M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) = u(t)
\end{equation}
where $u(t)\in\mathbb{R}^n$ is control input vector, $x(t)\in\mathbb{R}^n$ is state vector, $M(\cdot)\in\mathbb{R}^{n\times n}$ is inertia matrix, and $H(\cdot, \cdot)\in\mathbb{R}^n$ is non-inertial force vector. The control law is given as:
\begin{equation} \label{eq:control}
    u(t)= M(r(t))(\ddot{r}(t) + u_{fb}(t)) + H(r(t),\dot{r}(t)) 
\end{equation}
where $M(r(t)),\ddot{r}(t),H(r(t),\dot{r}(t))$ are the feedfoward control terms for canceling system nonlinearity, and $u_{fb}(t)$ is the feedback control law for improving system robustness. To make the model more realistic, the following external disturbances encountered in actual scenarios are considered:
\begin{enumerate}
    \item For agent, there exists coupling effect due to co-channel interference in communication between agents \cite{9834947}.
    \item For agent, there exists cyber-attack on communication network between agents and ground station.
    \item For agent, there exists sensor noise.
    \item For UAV, there exists wind disturbance \cite{9075385}.
    \item For robot, there exists ground reaction force \cite{chen2013human}. 
\end{enumerate}
Let $x_{i,j}(t), i=1,2,\dots,N_T, j=1,2,\dots,N_A$ denote the state vector of agents $\alpha_{i,j}$.The coupling term can be represented as \begin{equation} \label{eq:UAV couple}
    \sum_{k = 1, k \neq i}^{N_T}f_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)
\end{equation} for UAVs $\alpha_{i, 1}$ and \begin{equation} \label{eq:robot couple}
    \sum_{k = 1, k \neq j'}^{N_A}f_{i, j', k}(x_{i, j'}(t))x_{i, k}(t)
\end{equation} for robots $\alpha_{i, j'}$ where $j'=2,3,...,N_A$ \cite{9834947}.

Since the ground station is responsible for the calculation, the calculated control command (\ref{eq:control}) will be transmitted to the agent through the network channel in URTS. Therefore, the coupling effect due to co-channel interference and the cyber-attack signal will deteriorate the control command. In addition, the wind disturbance and the ground reaction force will apply extra force on an agent (\ref{eq:agent}). Therefore, through appropriate conversion, the above disturbances can be equivalent to a disturbance force $d_1(t)$. The nominal system (\ref{eq:agent}) then be rewrited as the following real system:
% The coupling effect for an agent \textit{$agent_{i,j}$} in URTS can be expressed as the form $\sum_{i'=1,i'\neq i}^{N_i}\sum_{j'=1,j'\neq j}^{N_j}\textit{c}_{i,j}(x_{i,j}(t))\times x_{i',j'}(t)$ where $x_{i,j}(t)$ is the own state.
\begin{equation} \label{eq:agent d1} 
    M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) = u(t) + d_1(t)
\end{equation}
% \subsubsection{Internal uncertainties}
% In practice, there is uncertaintiey in the parameters of inertia matrix $M$, Coriolis and centripetal force vector $C$, gravitational force vector $G$, and friction vector $F$. Its effect can be expressed as:
% \begin{equation} \label{eq:internal}
%     \begin{split}
%         &M = M_0 + \Delta M, C = C_0 + \Delta C
%         \\
%         &G = G_0 + \Delta G, F = F_0 + \Delta F
%     \end{split}
% \end{equation}
% where $M_0, C_0, G_0$ and  $F_0$ is the nominal part and $\Delta M,\Delta C,\Delta G$ and $\Delta F$ is the uncertain part.
Now, substituting (\ref{eq:control}) into (\ref{eq:agent d1}) and subtracting $M(x(t))\ddot{r}(t)$ from the left and right sides, we have:
\begin{equation} \label{eq:agent1}
    \begin{split}
        & M(x(t))(\ddot{x}(t)-\ddot{r}(t)) + H(x(t),\dot{x}(t)) \\
        & =(M(r(t))-M(x(t)))\ddot{r}(t) + M(r(t))u_{fb}(t) \\
        & + H(r(t),\dot{r}(t)) + d_1(t)
    \end{split}
\end{equation}
By Multipling $M(x(t))^{-1}$ from the left and right sides and with some arrangments, we have:
\begin{equation} \label{eq:error, state eq}
    \ddot{e}(t) = u_{fb}(t) + f_1(t)
\end{equation}
where $f_1(t) = M(x(t))^{-1}(-\Delta M (\ddot{r}(t)+u_{fb}(t)) -\Delta H + d_1(t))\in\mathbb{R}^n$ is the actuator fault signal, $\Delta M \triangleq M(x(t)) - M(r(t)), \Delta H \triangleq H(x(t),\dot{x}(t)) - H(r(t),\dot{r}(t))$ are the error terms from feedforward compensation, and $e(t)= x(t)-r(t)$ is the tracking error.
% \textit{
%     \begin{remark}
%         Although the error terms $\Delta e$, $\Delta M$ and $\Delta H$ caused by the difference between state $x(t)$ and estimated state $\hat{x}(t)$ are not necessarily bounded, they can still be estimated as long as they are smooth.
%     \end{remark}
% }
Let $\pmb{e}(t)=\begin{bmatrix}
    \int_{0}^{t}e^T(\tau)d\tau & e^T(t) & \dot{e}^T(t)
\end{bmatrix}^T\in\mathbb{R}^{3n}$ be the PID tracking error, (\ref{eq:error, state eq}) can be rewrited as:
\begin{equation} \label{eq:linear f1}
    \dot{\pmb{e}}(t)=A\pmb{e}(t)+B(u_{fb}(t)+f_1(t))
\end{equation}
where $ A = A_0\otimes I_n, B = B_0\otimes I_n$
with $A_0 = \begin{bmatrix}
    0 & 1 & 0 \\ 0 & 0 & 1 \\ 0 & 0 & 0
\end{bmatrix}, B_0 = \begin{bmatrix}
0 \\ 0 \\ 1
\end{bmatrix}$.

@@

\textit{Agents:}\begin{enumerate}
    \item system parameters: $C_0 = I_3$, $B_{2,0} = [0, 0.1, 1]^T$.
    \item designed parameters: $Q_1 = 50*diag(diag(1,100,10),\allowbreak 0, 0), Q_2 = 5*diag(diag([1,100,10]), diag(1,0.1,\allowbreak 0.01), diag(1,0.1,0.01 ,0.001)), R=0.002, \rho=30$. Actuator and sensor smoothing signal model window sizes are $3$ and $4$, respectively.
\end{enumerate}

@@

\textit{Robots:} \begin{enumerate}
    \item system parameters: Appendix E in \cite{ourrobot}. Initial values $\bar{x}_0=$.
    \item designed parameters: $Q_1=,Q_2=,R=,rho=20$.
\end{enumerate}

@@

\textit{UAV:}
The trajectories of reference, state and estimated state are shown in Fig. \ref{fig:UAV, state}. The estimation of actuator fault $f_1(t)\in\mathbb{R}^6$ is shown in Fig. \ref{fig:UAV, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t) = [10\sin(3t),...,10\sin(3t)]^T + \sum_{k = 1, k \neq i}^{N_T}f_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)$, i.e., the non-couple term and the couple term in (\ref{eq:UAV couple}). Let $x_{i, 1}(t) = [x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t)]^T$, then $f_{i, 1, k}(x_{i, 1}(t)) = 0.1diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t))$. The estimation of sensor fault $f_2(t)$ is shown in Fig. \ref{fig:UAV, fs} where $f_2(t)$ is set as a smoothed square wave as shown in figure. The control effort is shown in Fig. \ref{fig:UAV, control}.
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The trajectories of reference, state and estimated state of the UAV $\alpha_{i,1}$}%
    \label{fig:UAV, state}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of actuator fault of the UAV $\alpha_{i,1}$}
    \label{fig:UAV, fa}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of snesor fault of the UAV $\alpha_{i,1}$}%
    \label{fig:UAV, fs}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The control effort of the UAV $\alpha_{i,1}$}%
    \label{fig:UAV, control}
\end{figure}

\textit{Robot:}
The trajectories of reference, state and estimated state are shown in Fig. \ref{fig:robot, state}.
The estimation of actuator fault $f_1(t)\in\mathbb{R}^{12}$ is shown in Fig. \ref{fig:robot, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t) = [\sin(3t),...,\sin(3t)]^T + \sum_{k = 1, k \neq j'}^{N_A}f_{i, j', k}(x_{i, j'}(t))x_{i, k}(t)$, i.e., the non-couple term and the couple term in (\ref{eq:robot couple}). Let $x_{i, j'}(t) = [x_{i, j', 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, j', 12}(t)]^T$, then $f_{i, j', k}(x_{i, j'}(t)) = 0.01diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 12}(t))$.

The estimation of actuator fault $f_1(t)$ is shown in Fig. \ref{fig:robot, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t)=\sin(3t)$. The estimation of sensor fault $f_2(t)$ is shown in Fig. \ref{fig:robot, fs} where $f_2(t)$ is set as a smoothed square wave as shown in figure. The control effort is shown in Fig. \ref{fig:robot, control}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{i,2}$}%
    \label{fig:robot, state}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of actuator fault of the robot $\alpha_{i,2}$.}%
    \label{fig:robot, fa}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of sensor fault of the robot $\alpha_{i,2}$}%
    \label{fig:robot, fs}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The control effort of the robot $\alpha_{i,2}$}%
    \label{fig:robot, control}
\end{figure}
